Generalized Tractability

### 2023-05-13 GeneralizedTractability_230501.tex
Updates from Overleaf

Certain common notions of tractability are covered by the general situation described above.
{\small
\begin{equation*}
	\begin{array}{r@{\quad}c@{\quad}cc}
		\text{Tractability type} & T(\varepsilon^{-1},d,\vp)
		& T(0,d,\vp)\\
		\toprule
		\text{strong polynomial algebraic} & \max(1,\varepsilon^{-p}) & 1\\
		\text{polynomial algebraic} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
		\text{strong polynomial exponential} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
		\text{polynomial exponential } &
		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q} \\
        \text{quasi-polynomial algebraic} & 
        \exp\{p(1+\log(\max(1,\varepsilon^{-1}))(1+\log(d))\} &
        \exp\{p(1+\log(d))\}\\
        \text{quasi-polynomial exponential} & 
        \exp\{p(1+\log(1+\log(\max(1,\varepsilon^{-1})))(1+\log(d))\} &
        \exp\{p(1+\log(d))\}
	\end{array}
\end{equation*}}

@@

\begin{example}[Algebraic polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}\, d^q
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where in this case $\vp = (p,q)$.
Then Theorem \ref{thm_main_tract2} yields the  equivalent condition for algebraic polynomial tractability:
\[
 \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{p,q} \in \naturals.
\]
Furthermore, the set of optimal $(p,q)$ is a subset of
\begin{multline*}
\{(p^*,q^*) : \text{the above condition holds for all }(p,q) \in (p^*,\infty) \times (q^*,\infty) \\
\text{but not for any }(p,q) \in [0,p^*/2) \times [0,q^*/2)\}.
\end{multline*}
This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NW08} \fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NW08}}.
\end{example}

\begin{example}[Strong exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\]
where $\vp$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for strong exponential polynomial tractability \[
 \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty.
\] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
\end{example}
\begin{example}[Exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability
\[
 \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p d^{-q} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
\end{example}

@@

\noindent Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log d)\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\] where in this case $\vp = p$. This can be rewritten as 
\[
T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
\]
Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$. Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
\[
\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
\]
\end{example}
\begin{example}[Exponential quasi-polynomial tractability]

\noindent Suppose that the tractability function, $T$, is defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log d)\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\] where in this case $\vp = p$. This can be rewritten as 
\[
T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p
\]
Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$. Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for quasi-polynomial tractability in the exponential case
\[
\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty
\]
\end{example}

\kachi{In the following we introduce two specific cases of tractability which depend on the form of the function $T$.
\begin{example}[(Strong) Separable tractability]
Suppose that
\[
 T(\varepsilon^{-1},d,\vp)= \phi(\varepsilon^{-1},p)\, \psi(d,q)
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty).
\]
with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ and where $\vp = (p,q)$.

%In addition, we assume the following conditions as in (\ref{eq:ptauassume}). That is, there exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
%\begin{equation} \label{eq:tractiff}    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p))} < \infty.\end{equation}

 %\begin{align*}
  %   [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}

Observe that for this tractability function $T$, we have strong tractability if the following condition is satisfied
\[
 T(\varepsilon^{-1},1,\vp)= \phi(\varepsilon^{-1},p)\, \psi(1,0) = \phi(\varepsilon^{-1},p)
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \ge 0,
\] where in this case $\vp$ is a scalar. Furthermore, we assume the following technical conditions. There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
\end{align*}
Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
\begin{equation*} \label{eq:strong_tractiff}
     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
\end{equation*}
Theorem \ref{thm_main_tract2} yields the following equivalent condition for 
separable tractability
\[
 \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = L_{(p,q)\psi(d,q)}}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
\]
%As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated. 
\end{example}
\begin{example}[Non-separable symmetric tractability]
    Let the tractability function $T$, be defined by
\[
 T(\varepsilon^{-1},d,(p,q))= \exp\{\phi(\varepsilon^{-1},p)\, \psi(d,q)\}
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p\ge 0.
\]  with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$. Furthermore, we assume the following technical conditions. There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
\end{align*}
\end{example}
}

@@

Suppose that the domain of interesting $(\varepsilon^{-1},d)$ is not all of $(0,\infty \times \naturals$ but given by 
\begin{equation}
    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon > E(d) \ge 0, \ d \in \naturals \},
\end{equation}
where $E$ is a non-increasing function.  A problem is
$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:rest_strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
\end{equation}
Define $M(d) = \max\{n : \lambda_{n+1,d} \ge E(d)\}$, i.e., 
\[
\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d)+1,d} \ge E(d) > \lambda_{M(d)+2,d}, \qquad
(\lambda_{1,d}^{-1},d), \cdots, (\lambda^{-1}_{M(d)+1,d},d) \} \in \Omega.
\]

>>>>

Certain common notions of tractability are covered by the general situation described above.
{\small
\begin{equation*}
	\begin{array}{r@{\quad}c@{\quad}cc}
		\text{Tractability type} & T(\varepsilon^{-1},d,\vp)
		& T(0,d,\vp)\\
		\toprule
		\text{strong polynomial algebraic} & \max(1,\varepsilon^{-p}) & 1\\
		\text{polynomial algebraic} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
		\text{strong polynomial exponential} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
		\text{polynomial exponential } &
		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q} \\
        \text{quasi-polynomial algebraic} & 
        \exp\{p(1+\log(\max(1,\varepsilon^{-1}))(1+\log(d))\} &
        \exp\{p(1+\log(d))\}\\
        \text{quasi-polynomial exponential} & 
        \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log(d))\} &
        \exp\{p(1+\log(d))\}
	\end{array}
\end{equation*}}

@@

\begin{example}[Algebraic polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}\, d^q
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where in this case $\vp = (p,q)$.
Then Theorem \ref{thm_main_tract2} yields the  equivalent condition for algebraic polynomial tractability:
\[
 \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
Furthermore, the set of optimal $(p,q)$ is a subset of
\begin{multline*}
\{(p^*,q^*) : \text{the above condition holds for all }(p,q) \in (p^*,\infty) \times (q^*,\infty) \\
\text{but not for any }(p,q) \in [0,p^*/2) \times [0,q^*/2)\}.
\end{multline*}
This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NW08} \fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NW08}}.
\end{example}

\begin{example}[Strong exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\]
where $\vp$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for strong exponential polynomial tractability \[
 \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals
\] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
\end{example}
\begin{example}[Exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability
\[
 \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p d^{-q} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
\end{example}

@@

\noindent Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\] where in this case $\vp = p$. This can be rewritten as 
\[
T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
\]
Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$. Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
\[
\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
\]
\end{example}
\begin{example}[Exponential quasi-polynomial tractability]

\noindent Suppose that the tractability function, $T$, is defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\] where in this case $\vp = p$. This can be rewritten as 
\[
T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p
\]
Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$. Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for quasi-polynomial tractability in the exponential case
\[
\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty
\]
\end{example}

\kachi{In the following we introduce two specific cases of tractability which depend on the form of the function $T$.
\begin{example}[(Strong) Separable tractability]
Suppose that
\[
 T(\varepsilon^{-1},d,\vp)= \phi(\varepsilon^{-1},p)\, \psi(d,q)
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2.
\]
with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ and where $\vp = (p,q)$.

We say that a problem is defined as $T$-separable tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq  C_{\vp}\,T(\varepsilon^{-1},d,\vp)\qquad \forall \varepsilon >0, \, d\in\naturals,
\]
that is
\[
\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\, \psi(d,q) \qquad \forall \varepsilon >0, \, d\in\naturals.
\]
A problem is strongly $T$-separable tractable with parameter $\vp$ iff the complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq C_{\vp}T(\varepsilon^{-1}, 1,\vp) \qquad \forall \varepsilon >0, \, d\in\naturals,
\] where $\vp = p$. We have
\[
\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals.
\]
%In addition, we assume the following conditions as in (\ref{eq:ptauassume}). That is, there exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
%\begin{equation} \label{eq:tractiff}    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p))} < \infty.\end{equation}
Furthermore, we assume that
\[
\lim_{\varepsilon\rightarrow0}T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d\in\naturals, \vp \in[0,\infty)^2.
\]
Also since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit
\[
T(0,d,\vp):= \lim_{\varepsilon \rightarrow \infty}T(\varepsilon^{-1},d,\vp)\geq T(0,1,\textbf{0})>0
\] 
%Furthermore, we assume the following technical conditions. There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
\end{align*}
%\begin{align*}
 %  [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}
Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
\begin{equation*} \label{eq:strong_tractiff}
     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
\end{equation*}
Theorem \ref{thm_main_tract2} yields the following equivalent condition for 
separable tractability
\[
 \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = L_{(p,q)\psi(d,q)}}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
\]
%As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated. 
\end{example}
\begin{example}[Non-separable tractability]
    Let the tractability function $T$, be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp\{p(\phi(\varepsilon^{-1})\, \psi(d))\}
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp\in [0,\infty).
\]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$ and $\vp = p$. Furthermore, we assume the following technical conditions. There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
\end{align*}
\end{example}
}

@@

Suppose that the domain of interesting $(\varepsilon^{-1},d)$ is not all of $(0,\infty \times \naturals$ but given by 
\begin{equation}
    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon > E(d) \ge 0, \ d \in \naturals \},
\end{equation}
where $E$ is a non-increasing function.  A problem is
$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:rest_strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
\end{equation}
Define $M(d) = \max\{n : \lambda_{n+1,d} \ge E(d)\}$, i.e., 
\[
\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d)+1,d} \ge E(d) > \lambda_{M(d)+2,d}, \qquad
(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d)+1,d},d)  \in \Omega.
\]
